Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-08 programming23/artifact/main.tex
artifact data

\usepackage{graphicx}
\usepackage[margin=2cm]{geometry}
\usepackage{verbatim}
\usepackage[export]{adjustbox}

@@

\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}

@@

\begin{minipage}{0.5\columnwidth}
  \textbf{Lines:}\\
  \includegraphics[width=\columnwidth]{out/lines-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Edit Range:}\\
  \includegraphics[width=\columnwidth]{out/editrange-distribution.pdf}
\end{minipage}

@@

Lines 9-13 of \texttt{out/overview.txt} partition sessions and report on upgrades and downgrades,
\emph{but} the final two numbers are incorrect (upgrade and downgrade) because they include
module switches:

@@

% \includeverbatim{out/downgrade-count.txt}

% TODO

@@

TODO

@@

Output from \texttt{code/type-error-count.rkt}
run on \texttt{code/te-editrange-ss-*.rktd}:

TODO

@@

\includegraphics[width=0.8\columnwidth]{out/error-count-nocheck-row--te-density-diff.pdf}
\includegraphics[width=0.8\columnwidth]{out/error-count-nonstrict-row--te-density-diff.pdf}
\includegraphics[width=0.8\columnwidth]{out/error-count-strict-row--te-density-diff.pdf}

@@

Shuffled text output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}:

>>>>

\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage[margin=2cm]{geometry}
\usepackage{verbatim}
\usepackage[export]{adjustbox}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\pct}[1]{$#1\,\%$}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\let\midrule=\hrule

@@

\begin{minipage}{0.5\columnwidth}
  \textbf{Lines:}\\
  \includegraphics[width=0.4\columnwidth]{out/lines-distribution.pdf}
\end{minipage}\begin{minipage}{0.5\columnwidth}
  \textbf{Edit Range:}\\
  \includegraphics[width=0.4\columnwidth]{out/editrange-distribution.pdf}
\end{minipage}

@@

Lines 9-13 of \texttt{out/overview.txt} partition sessions and report on upgrades and downgrades,
\emph{but} the final two numbers are incorrect (upgrade and downgrade) because they include
data from module switches:

@@

Output:

\verbatiminput{out/downgrade-count.txt}

@@

\begin{tabular}{lr@{~}r@{~}rr@{~}r@{~}rr@{~}r@{~}r}
  & \zerowidth{\mnocheck{}} & & & \zerowidth{\mnonstrict{}} & & & \zerowidth{\mstrict{}} & & \\
  & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} & \rcell{Add} & \ycell{Keep} & \gcell{Drop} \\\hline
  TypeMismatch & {0} & {0} & {0} & {103} & {51} & {80} & {13} & {6} & {18} \\
  UnknownSymbol & {0} & {0} & {0} & {1992} & {438} & {1797} & {38} & {18} & {35} \\
  UnknownProperty & {0} & {0} & {0} & {256} & {156} & {208} & {16} & {18} & {22} \\
  NotATable & {0} & {0} & {0} & {4} & {1} & {5} & {2} & {0} & {1} \\
  CannotExtendTable & {0} & {0} & {0} & {6} & {8} & {1} & {0} & {0} & {1} \\
  OnlyTablesCanHaveMethods & {0} & {0} & {0} & {0} & {0} & {2} & {0} & {0} & {0} \\
  DuplicateTypeDefinition & {0} & {0} & {0} & {1} & {0} & {0} & {0} & {0} & {0} \\
  CountMismatch & {0} & {0} & {0} & {184} & {42} & {157} & {9} & {2} & {9} \\
  FunctionDoesNotTakeSelf & {0} & {0} & {0} & {3} & {4} & {1} & {0} & {0} & {0} \\
  OccursCheckFailed & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {0} & {1} \\
  UnknownRequire & {0} & {0} & {0} & {43} & {30} & {37} & {5} & {3} & {3} \\
  IncorrectGenericParameterCount & {0} & {0} & {0} & {0} & {0} & {0} & {1} & {0} & {1} \\
  SyntaxError & {0} & {0} & {8290} & {0} & {0} & {1149} & {0} & {0} & {29} \\
  UnknownPropButFoundLikeProp & {0} & {0} & {0} & {20} & {17} & {13} & {0} & {0} & {0} \\
  GenericError & {0} & {0} & {0} & {177} & {47} & {149} & {5} & {0} & {8} \\
  CannotCallNonFunction & {0} & {0} & {0} & {12} & {2} & {13} & {1} & {0} & {1} \\
  ExtraInformation & {0} & {0} & {0} & {46} & {6} & {33} & {1} & {0} & {1} \\
  ModuleHasCyclicDependency & {0} & {0} & {0} & {9} & {5} & {8} & {0} & {0} & {0} \\
  IllegalRequire & {0} & {0} & {0} & {7} & {1} & {11} & {0} & {0} & {0} \\
  FunctionExitsWithoutReturning & {0} & {0} & {0} & {6} & {1} & {5} & {7} & {3} & {5} \\
  CannotInferBinaryOperation & {0} & {0} & {0} & {0} & {1} & {0} & {5} & {6} & {6} \\
  MissingProperties & {0} & {0} & {0} & {8} & {3} & {6} & {5} & {3} & {3} \\
  OptionalValueAccess & {0} & {0} & {0} & {21} & {45} & {15} & {4} & {2} & {4} \\
\end{tabular}

@@

Output from \texttt{code/type-error-count.rkt}
run on \texttt{code/te-editrange-ss-*.rktd}.

This script produces output for all three modes: \mnocheck{}, \mnonstrict{}, and \mstrict{}.
The paper combines \mnonstrict{} and \mstrict{} into one table.

\subsubsection*{\mnocheck{}}

unused code IllegalRequire
unused code UnknownSymbol
unused code TypeMismatch
unused code NormalizationTooComplex
unused code DynamicPropertyLookupOnClassesUnsafe
unused code MissingUnionProperty
unused code UnknownProperty
unused code TypePackMismatch
unused code DuplicateTypeDefinition
unused code UnknownRequire
unused code TypesAreUnrelated
unused code MissingProperties
unused code FunctionExitsWithoutReturning
unused code CannotExtendTable
unused code FunctionDoesNotTakeSelf
unused code UnificationTooComplex
unused code GenericError
unused code NotATable
unused code OnlyTablesCanHaveMethods
unused code CodeTooComplex
unused code InternalError
unused code FunctionRequiresSelf
unused code UnknownPropButFoundLikeProp
unused code CannotInferBinaryOperation
unused code IncorrectGenericParameterCount
unused code OptionalValueAccess
unused code DuplicateGenericParameter
unused code CountMismatch
unused code OccursCheckFailed
unused code DeprecatedApiUsed
unused code CannotCallNonFunction
unused code ModuleHasCyclicDependency
unused code SwappedGenericTypeParameter
unused code ExtraInformation
NEVER APPEAR: (IllegalRequire UnknownSymbol TypeMismatch NormalizationTooComplex DynamicPropertyLookupOnClassesUnsafe MissingUnionProperty UnknownProperty TypePackMismatch DuplicateTypeDefinition UnknownRequire TypesAreUnrelated MissingProperties FunctionExitsWithoutReturning CannotExtendTable FunctionDoesNotTakeSelf UnificationTooComplex GenericError NotATable OnlyTablesCanHaveMethods CodeTooComplex InternalError FunctionRequiresSelf UnknownPropButFoundLikeProp CannotInferBinaryOperation IncorrectGenericParameterCount OptionalValueAccess DuplicateGenericParameter CountMismatch OccursCheckFailed DeprecatedApiUsed CannotCallNonFunction ModuleHasCyclicDependency SwappedGenericTypeParameter ExtraInformation)

\begin{tabular}{lr}
  \code{SyntaxError} & \pct{100.00} \\
\end{tabular}

\subsubsection*{\mnonstrict{}}

unused code NormalizationTooComplex
unused code DynamicPropertyLookupOnClassesUnsafe
unused code TypePackMismatch
unused code UnificationTooComplex
unused code CodeTooComplex
unused code InternalError
unused code FunctionRequiresSelf
unused code IncorrectGenericParameterCount
unused code DuplicateGenericParameter
unused code OccursCheckFailed
unused code DeprecatedApiUsed
unused code SwappedGenericTypeParameter
NEVER APPEAR: (NormalizationTooComplex DynamicPropertyLookupOnClassesUnsafe TypePackMismatch UnificationTooComplex CodeTooComplex InternalError FunctionRequiresSelf IncorrectGenericParameterCount DuplicateGenericParameter OccursCheckFailed DeprecatedApiUsed SwappedGenericTypeParameter)

\begin{tabular}{lr}
  \code{UnknownSymbol} & \pct{62.13} \\
  \code{SyntaxError} & \pct{15.42} \\
  \code{UnknownProperty} & \pct{8.28} \\
  \code{UnknownRequire} & \pct{3.13} \\
  \code{TypeMismatch} & \pct{2.44} \\
  \code{CountMismatch} & \pct{2.26} \\
  \code{OptionalValueAccess} & \pct{2.07} \\
  \code{GenericError} & \pct{2.06} \\
  \code{UnknownPropButFoundLikeProp} & \pct{0.44} \\
  \code{CannotExtendTable} & \pct{0.42} \\
  \code{ExtraInformation} & \pct{0.32} \\
  \code{ModuleHasCyclicDependency} & \pct{0.23} \\
  \code{IllegalRequire} & \pct{0.20} \\
  \code{NotATable} & \pct{0.15} \\
  \code{CannotCallNonFunction} & \pct{0.15} \\
  \code{MissingProperties} & \pct{0.09} \\
  \code{FunctionExitsWithoutReturning} & \pct{0.07} \\
  \code{FunctionDoesNotTakeSelf} & \pct{0.07} \\
  \code{MissingUnionProperty} & \pct{0.02} \\
  \code{CannotInferBinaryOperation} & \pct{0.02} \\
  \code{OnlyTablesCanHaveMethods} & \pct{0.01} \\
  \code{DuplicateTypeDefinition} & \pct{0.00} \\
  \code{TypesAreUnrelated} & \pct{0.00} \\
\end{tabular}

\subsubsection*{\mstrict{}}

unused code NormalizationTooComplex
unused code DynamicPropertyLookupOnClassesUnsafe
unused code MissingUnionProperty
unused code TypePackMismatch
unused code DuplicateTypeDefinition
unused code FunctionDoesNotTakeSelf
unused code UnificationTooComplex
unused code OnlyTablesCanHaveMethods
unused code CodeTooComplex
unused code InternalError
unused code FunctionRequiresSelf
unused code DuplicateGenericParameter
unused code DeprecatedApiUsed
unused code SwappedGenericTypeParameter
NEVER APPEAR: (NormalizationTooComplex DynamicPropertyLookupOnClassesUnsafe MissingUnionProperty TypePackMismatch DuplicateTypeDefinition FunctionDoesNotTakeSelf UnificationTooComplex OnlyTablesCanHaveMethods CodeTooComplex InternalError FunctionRequiresSelf DuplicateGenericParameter DeprecatedApiUsed SwappedGenericTypeParameter)

\begin{tabular}{lr}
  \code{UnknownSymbol} & \pct{23.97} \\
  \code{TypeMismatch} & \pct{20.46} \\
  \code{UnknownProperty} & \pct{18.88} \\
  \code{SyntaxError} & \pct{9.31} \\
  \code{CannotInferBinaryOperation} & \pct{6.94} \\
  \code{MissingProperties} & \pct{4.04} \\
  \code{FunctionExitsWithoutReturning} & \pct{2.99} \\
  \code{OptionalValueAccess} & \pct{2.99} \\
  \code{CountMismatch} & \pct{2.99} \\
  \code{UnknownRequire} & \pct{2.37} \\
  \code{GenericError} & \pct{2.28} \\
  \code{NotATable} & \pct{1.32} \\
  \code{ExtraInformation} & \pct{0.35} \\
  \code{UnknownPropButFoundLikeProp} & \pct{0.26} \\
  \code{IllegalRequire} & \pct{0.18} \\
  \code{IncorrectGenericParameterCount} & \pct{0.18} \\
  \code{CannotCallNonFunction} & \pct{0.18} \\
  \code{TypesAreUnrelated} & \pct{0.09} \\
  \code{CannotExtendTable} & \pct{0.09} \\
  \code{OccursCheckFailed} & \pct{0.09} \\
  \code{ModuleHasCyclicDependency} & \pct{0.09} \\
\end{tabular}

@@

\includegraphics[width=0.8\columnwidth]{out/error-count-nocheck-row--te-density-diff.pdf}

\includegraphics[width=0.8\columnwidth]{out/error-count-nonstrict-row--te-density-diff.pdf}

\includegraphics[width=0.8\columnwidth]{out/error-count-strict-row--te-density-diff.pdf}

@@

From reordered text output from \texttt{code/error-count.rkt}
on \texttt{out/error-density-ss-*.rktd}:
